Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-12-20 paper/main.tex
section function mods

In category theory, a presheaf \sheafc\, is generalized to be a contravariant functor\cite{nlab:presheaf} from a category to a set. 
\begin{equation}
  \label{eq:actc:sheaf}
 \sheafc: \textcolor{source}{\mathcal{C}^{op}} \rightarrow \setc
\end{equation}
We can define natural transforms, introduced in \autoref{eq:related-work:equivariance:natural-transform}, between sheaves over different spaces, for example spaces representing the topology of the data and the graphic, because sheaves can be moved over different topological spaces if there is a map between those spaces. 
Given a map $\textcolor{functor}{f}:\textcolor{source}{X} \textcolor{functor}{\rightarrow} \textcolor{target}{Y}$ between topological spaces $\textcolor{source}{X}, \textcolor{target}{Y}$ and sheaves on each space $\sheafc_{\textcolor{source}{X}}, \sheafc_{\textcolor{target}{Y}}$, we can construct a pullback functor $f^*$ and pushforward functor $f_*$ \cite{harder2008lectures} that can be composed with the sheaf functors. 
\begin{equation}
  \label{eq:atct:pullback-pushforward}
  \begin{tikzcd}[row sep=huge]
    \sheafc_{\textcolor{source}{X}}(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f_*}", color=functor]                            &  & (\textcolor{functor}{f_*}\sheafc_{\textcolor{source}{X}})(\textcolor{target}{Y})    \\
    \textcolor{source}{X} \arrow[rr, "\textcolor{functor}{f}", color=functor] \arrow[u, "\sheaf_{\textcolor{source}{X}}", color=sheaf] \arrow[d, dashed, color=sheaf] &  & \textcolor{target}{Y} \arrow[d, "\sheaf_{\textcolor{target}{Y}}", color=sheaf] \arrow[u, dashed, color=sheaf] \\
    (\textcolor{functor}{f^*}\sheafc_{\textcolor{target}{Y}})(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f^*}", color=functor]  &  & \sheafc_{\textcolor{target}{Y}}(\textcolor{target}{Y})                             
  \end{tikzcd}
\end{equation}
As shown in \autoref{eq:atct:pullback-pushforward}, the composition $f_*\sheaf_{X}$ modifies the functor $\sheaf_{X}$ such that sections $\dsection \in \sheaf_{X}

>>>>

In category theory, a presheaf \sheafc\, is generalized to be a contravariant functor\cite{nlab:presheaf} from a category to a set. 
\begin{equation}
  \label{eq:actc:sheaf}
 \sheafc: \textcolor{source}{\mathcal{C}^{op}} \rightarrow \setc
\end{equation}
We can define natural transforms, introduced in \autoref{eq:related-work:equivariance:natural-transform}, between sheaves over different spaces, for example spaces representing the topology of the data and the graphic, because sheaves can be moved over different topological spaces if there is a map between those spaces. 
Given a map $\textcolor{functor}{f}:\textcolor{source}{X} \textcolor{functor}{\rightarrow} \textcolor{target}{Y}$ between topological spaces $\textcolor{source}{X}, \textcolor{target}{Y}$ and sheaves on each space $\sheafc_{\textcolor{source}{X}}, \sheafc_{\textcolor{target}{Y}}$, we can construct a pullback functor $f^*$ and pushforward functor $f_*$ \cite{harder2008lectures} that can be composed with the sheaf functors. 
\begin{equation}
  \label{eq:atct:pullback-pushforward}
  \begin{tikzcd}[row sep=huge]
    \sheafc_{\textcolor{source}{X}}(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f_*}", color=functor]                            &  & (\textcolor{functor}{f_*}\sheafc_{\textcolor{source}{X}})(\textcolor{target}{Y})    \\
    \textcolor{source}{X} \arrow[rr, "\textcolor{functor}{f}", color=functor] \arrow[u, "\sheaf_{\textcolor{source}{X}}", color=sheaf] \arrow[d, dashed, color=sheaf] &  & \textcolor{target}{Y} \arrow[d, "\sheaf_{\textcolor{target}{Y}}", color=sheaf] \arrow[u, dashed, color=sheaf] \\
    (\textcolor{functor}{f^*}\sheafc_{\textcolor{target}{Y}})(\textcolor{source}{X}) \arrow[rr, "\textcolor{functor}{f^*}", color=functor]  &  & \sheafc_{\textcolor{target}{Y}}(\textcolor{target}{Y})                             
  \end{tikzcd}
\end{equation}
As shown in \autoref{eq:atct:pullback-pushforward}, the pushforward $f_*\sheaf_{X}$ modifies the sheaf $\sheaf_{X}$ such that sections $s \in \sheaf_{X}(X)$ can be evaluated over points in $y$
\begin{equation}
  \label{eq:atct:pushforward-section}
  (s: x \rightarrow \setb) \xrightarrow{f_*} (s_*: y \rightarrow \setb)
\end{equation}
while the pullback functor $f^*$ modifies the sheaf  $\sheaf_{Y}$ such that sections $\t \in \sheaf_{Y}(Y)$ can be evaluated over points in $x$
\begin{equation}
  \label{eq:atct:pullback-section}
  (t^*: x \rightarrow \setb) \xrightarrow{f^*} (t: y \rightarrow \setb)
\end{equation}
As shown in \autoref{eq:atct:pushforward-section}, the pushforward modifies the signature of the functions returned by the functor , while in \autoref{eq:atct:pullback-section} the pullback modifies the signature of the argument to the functor.
